Algorithm Engineering

### 2022-11-09 Assignments/paper.tex
add code04

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

%\bibitem{ref_book1}
%Arpaci-Dusseau, Remzi H and Arpaci-Dusseau, Andrea C.: Operating systems: Three easy pieces. Arpaci-Dusseau Books LLCr,
 %(2018)

@@

\bibitem{ref_url2}
Armv8-A Address Translation pdf, \url{https://developer.arm.com/documentation/100940/0101/}.

>>>>

\subsection{How does ordered clause in OpenMP work in conjunction with a parallel loop?}
\subsection{What is the collapse clause in OpenMP good for?}
\subsection{Explain how reductions work internally in OpenMP}
\subsection{What is the purpose of a barrier in parallel computing?}
\subsection{Explain the difference between the library routines: omp\_get\_num\_threads(), omp\_get\_num\_procs() and omp\_get\_max\_threads().}
\subsection{Clarify how the storage attributes private and firstprivate differ from each other.}
\subsection{Write in pseudo code how the computation of pi can be parallelized with simple threads.}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

@@
